\textcolor{r_s}{Displacement Detection Based on Bayesian Inference from GNSS Kinematic Positioning for Deformation Monitoring}

### 2021-09-24 paper/r1/manuscript-mssp.tex
Response to Reviewers.docx

		\title{\textcolor{r_s}{Displacement Detection from GNSS Kinematic Positioning Using Bayesian Inference}}

		%% use optional labels to link authors explicitly to addresses:
		%% \author[label1,label2]{}
		%% \address[label1]{}
		%% \address[label2]{}
		\author[a]{Nan Shen}
		\author[a]{Liang Chen\corref{mycorrespondingauthor}}
		\cortext[mycorrespondingauthor]{Corresponding author}
		\ead{l.chen@whu.edu.cn}
		\author[a]{Ruizhi Chen}
		\address[a]{State Key Laboratory of Information Engineering in Surveying, Mapping and Remote Sensing, Wuhan University, Wuhan 430000, PR China}
		\begin{abstract}
		Displacement is an important parameter in engineering analysis in structural mechanics and geomechanics.
		For decades, displacement detection based on the Global navigation satellite system (GNSS) has increasingly been important for a wide range of applications, from landslide monitoring, subsidence survey, to industrial measurement. 
%		Most of the GNSS-based displacement detection methods in these applications are based on GNSS long-term static positioning results.
%		With the development of the Internet of Things (IoT), high-precision GNSS positioning, and GNSS-related transmission protocol, kinematic positioning results can be transmitted to the cloud in real-time.
		However, due to the influence of measurement noise, it is still a challenge to identify and extract displacement from GNSS kinematic positioning results.
		To resolve this, we propose a novel displacement detection approach with the purpose of identifying and extracting displacement from GNSS kinematic positioning.
		Specifically, we use the Bayesian inference to obtain the displacement change time from the coordinate time series of GNSS kinematic positioning. 
		%The likelihood function of the observation and the prior distribution of the parameters to be estimated are provided.
		%Finally, Bayesian inference was implemented by Markov Chain Monte Carlo (MCMC) sampling.
		By investigating the posterior distribution of the designed change point parameter, we can identify the change points.
		Furthermore, we derive the mean value from the posterior distribution of the mean parameter, and further obtain the displacement.
		Results from simulation and field experiments have demonstrated the effectiveness and flexibility of the proposed method.
		For significant displacement, it can be clearly identified; for small displacement, it can be identified by adding an interval constraint prior. The accuracy of up-displacement extraction from GNSS real-time kinematic positioning can reach within 2 mm in 15 minutes.		
		\end{abstract}

@@

	% 仿真实验中不同基于索引检测方法的指标值如图6所示。
	% 从中可以看出不同探测方法所采用的指标的数值范围不一致，但在所设计的突变处很明显。
	%  然而，想基于这些指标值自动将这些突变点识别出来，还需要额外的工作。
	%  另外，这些方法设计之初为了探测突变点，并未涉及位移提取。
	%  有学者，基于设计了基于这些指标的突变探测和位移提取方法，但实时过程复杂。
	%  相比而言，本文提出的方法是一种简单直接易于实现的一站式方法。
	The index values of different index-based detection methods in the simulation experiment are shown in Fig. \ref{fig_v_sim_idx}.
	It can be seen that the numerical range of indicators used by different \textcolor{r_s}{index-based} detection methods is not consistent, but all are obvious at the designed abrupt point.
	However, to automatically identify these abrupt points based on these index values, additional work is required, such as setting a certain threshold  \textcolor{r_s}{or detection window\cite{shen_shortterm2021}}.
	In addition, these methods were originally designed to detect abrupt points without involving displacement extraction.
	There are abrupt detection and displacement extraction methods based on these indicators, but the implementation process is complex\cite{shen_shortterm2021}.
	In contrast, the method proposed in this work is a simple, straightforward, and easy-to-implement one-stop method.
	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_sigma_sim_simple}
		\caption{Histogram of posterior sample of $\sigma$ in the simulation experiment.}
		\label{fig_v_sigma_sim_simple}
	\end{figure} 
	\begin{figure}[htbp]
	\centering
	\includegraphics[scale=0.45]{v_sim_idx}
	\caption{Index values of different index-based detection methods in simulation experiments.}
	\label{fig_v_sim_idx}
	\end{figure} 
	\subsection{Field Experiments}
	The experiments were carried out on the roof of a building on the campus of Wuhan University, and the equipment deployment is shown in Fig. \ref{fig_v_field_exp_config}. 
	A hard plank was pressed with large stones to ensure that the plank remains as fixed as possible during moving the object hanging on the plank. 
	One receiver antenna was fixed on the plank as a rover, and the other receiver antenna was installed on a tripod beside it as the base station. 
	Both antennas were connected to BD992 OEM boards on the table, and the OEM boards were connected to the laptops for data collection. 
	As shown in subgraphs (c) and (d), the height of the antenna was measured with a tape before and after each movement of the object hanging on the plank. 
	\textcolor{r_s}{
		The minimum scale of the tape is 1 mm, that is, the accuracy of the tape is 1 mm, and the estimated reading is 0.1 mm.
		Take five readings for each measurement to ensure the accuracy and reliability of the data.
	}
	Besides, markers are made on the ground and on the antenna respectively to ensure that the same position was referenced for each measurement. 
	The sampling frequency of the GNSS receiver is set to 1 Hz. 
	We did two experiments, each lasting nearly 45 minutes. 
	During the experiment, the object hanging on the board was manually moved several times.
	The displacement amplitude of the second experiment is smaller than that of the first experiment.
	The GNSS observation data collected above are processed by the open-source software RTKLIB\cite{takasu2011rtklib}. 
	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.5]{v_field_exp_config}
		\caption{Filed experiment configuration. (a) Overview; (b) Working platform; (c) Displacement control platform; (d) Displacement measurement by tape. }
		\label{fig_v_field_exp_config}
	\end{figure}

@@

	For such a short baseline, most of the errors can be eliminated by the double-difference observation. 
	As can be seen from Fig. \ref{fig_v_bd9_3_up_ts}, there are still some unmodeled errors, such as the multipath error that have not been eliminated. 
	\textcolor{r_s}{The RTK positioning results are served as the input of displacement detection}, and Bayesian inference is implemented by the MCMC sampling. 
	The histogram of the posterior sample of $\tau$ is shown in Fig. \ref{fig_v_bd9_3_up_tau}.
	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_bd9_3_up_tau}
		\caption{Posterior sample distribution of $\tau$ in field experiment 1.}
		\label{fig_v_bd9_3_up_tau}
	\end{figure} 
	From the posterior sample distribution of $\tau_2$ in Fig. \ref{fig_v_bd9_3_up_tau}, one of the change points can be identified as 1897 s. 
	According to the maximum value in the bar chart of the posterior sample of $\tau_1$, the change point is identified as 781 s.
	However, as can be seen from Fig. \ref{fig_v_bd9_3_up_tau}, there are two peaks in the posterior sample distribution of change point $\tau_1$.
	The main reason is that the displacement control device is not completely controllable, and the plank floats up and down when moving the object. 
	In addition, since the antenna is close to the ground, the antenna vibration caused by breeze or touch causes an increase in the multipath phase rate or fading frequency\cite{kelly2003characterization}. 
	The index values of different index-based detection methods in \textcolor{r_s}{the} field experiment 1 are shown in Fig. \ref{fig_v_exp1_idx}. At the abrupt point, each index value is no longer as clear as in the simulation experiment, which puts forward higher requirements for additional analysis of these indexes.
	The posterior sample histogram of the $\mu$ of each segment divided by the change point and the displacement measured by the tape are shown in Fig. \ref{fig_v_bd9_3_up_mu} and Table \ref{tab_measured_height_9_3}, respectively.
	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_exp1_idx}
		\caption{Index values of different index-based detection methods in field experiment 1.}
		\label{fig_v_exp1_idx}
	\end{figure} 
	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_bd9_3_up_mu}
		\caption{Histogram of posterior sample of $\mu$ in field experiment 1.}
		\label{fig_v_bd9_3_up_mu}
	\end{figure} 
	\begin{table}[htbp]
		\centering
		%	\fontsize{6.5}{8}\selectfont
		\begin{threeparttable}
			\caption{Measured height before and after each movement of the object hanging on the plank in field experiment 1, unit (mm).}
			\label{tab_measured_height_9_3}
			\begin{tabular}{ccccccccc}
				\toprule
				&&&\textbf{1}&\textbf{2}&\textbf{3}&\textbf{4}&\textbf{5}&\textbf{mean}\cr
				\midrule
				\multirow{3}*{Step 1} 
				& & ${h_0}$    &371.0&370.9&370.9&371.1&370.9&370.96\\
				& & ${h_1}$    &341.0&341.1&341.5&341.9&341.0&341.30\\
				& & $\Delta h$ & -30.0& -29.8& -29.4& -29.2& -29.9&-29.66\\
				\hline
				\multirow{3}*{Step 2} 
				& & ${h_0}$    &340.5&340.1&340.0&340.0&340.1&340.14\\
				& & ${h_1}$    &313.0&312.9&312.9&313.0&313.0&312.96\\
				& & $\Delta h$ &-27.5& -27.2& -27.1& -27.0& -27.1& -27.18\\
				\bottomrule
			\end{tabular}
		\end{threeparttable}
	\end{table}

	The $\mu_0$, $\mu_1$, and $\mu_2$ obtained by the mean of the posterior samples are -1446.03 mm, -1474.11 mm, and -1489.83 mm, respectively, and the two displacements obtained by the difference of these mean values are -28.08 mm, -15.72 mm, respectively. The two displacements measured by tape are -29.66 mm and -27.18 mm respectively. 
	To our surprise, the displacement difference between the two methods at the two change points is 1.58 mm and 11.46 mm, respectively. 
	The main reason is that the displacement control device is not fully controllable.
\textcolor{r_s}{
	As can be seen from Fig. \ref{fig_v_bd9_3_up_ts}, the time series fluctuates obviously near the abrupt displacement. To explore the possible causes, the number of satellites, geometric dilution of precision(GDOP), signal-to-noise ratio(SNR), and multipath are shown in Fig. \ref{fig_v_ndop_snrmp_9_3}. The number of satellites and GDOP changed when the displacement took place, which may be caused by the shielding of the antenna during operation. The SNR and multipath have also changed when the displacement takes place, possibly due to antenna vibration caused by touch or wind.}

	As shown in Fig. \ref{fig_v_bd9_3_up_sigma}, the estimated value of $\sigma$ is 12.58 mm through the posterior sample mean of $\sigma$.
	%我们发现此处变点后验样本中的两个峰值对于均值和标准差中没有出现。
	%主要原因是变点的峰值距离很近，对于划分的段没有很明显的影响，因此对后验均值和标准差的浮动没有很大影响。
	%而在现实中，这种情况是会发生的，例如滑坡或者沉降，整个位移变化过程需要一定的时间，存在多个变化点。
	%然而，我们可能更加关注主要变化点，后面通过加入额外先验来提升主要变化点的识别，弱化次要变化点。
	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{ndop_snrmp_9_3}
		\caption{Number of satellites, GDOP, SNR, multipath of experiment 1.}
		\label{fig_v_ndop_snrmp_9_3}
	\end{figure} 
	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_bd9_3_up_sigma}
		\caption{Histogram of posterior \textcolor{r_s}{samples} of $\sigma$ in field experiment 1.}
		\label{fig_v_bd9_3_up_sigma}
	\end{figure} 
	Different from the posterior sample distribution of $\tau$, there is only one peak value in the posterior sample distribution of $\mu$ and $\sigma$.
	The main reason is that the interval of the two peaks is very close, which has little influence on the posterior mean and standard deviation.
	In reality, multiple change points exist, such as multiple displacements in a short period in the process of landslide or settlement.
	However, more attention is paid to the primary change points.
	By adding a prior to the model to improve the identification of the primary change points, and weaken the influence of secondary change points will be discussed later.
	\subsubsection{Field Experiment 2}%rover_bd9_4 part(650)
	This experiment is similar to the previous one except that the displacement amplitude is smaller. 
	The coordinate time series is obtained by RTKLIB with the same processing strategy as the previous experiment, and the up component of the time series is shown in Fig. \ref{fig_v_bd9_4_up_ts}. 
	In this experiment, the displacement measured by tape is shown in Table \ref{tab_measured_height_9_4}.

@@

	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_bd9_4_up_tau_add_new_rule}
		\caption{Posterior sample distribution of $\tau$ in field experiment 2 with an interval constraint prior.}
		\label{fig_v_bd9_4_up_tau_add_new_rule}
	\end{figure} 
	\begin{figure}[htbp]
	\centering
	\includegraphics[scale=0.45]{v_exp2_idx}
	\caption{Index values of different index-based detection methods in field experiment 2.}
	\label{fig_v_exp2_idx}
	\end{figure} 
	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_bd9_4_up_mu_add_new_rule}
		\caption{Histogram of posterior sample of $\mu$ in field experiment 2 with an interval constraint prior.}
		\label{fig_v_bd9_4_up_mu_add_new_rule}
	\end{figure} 
	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_bd9_4_up_sigma_add_new_rule}
		\caption{Histogram of posterior \textcolor{r_s}{samples} of $\sigma$ in field experiment 2 with an interval constraint prior.}
		\label{fig_v_bd9_4_up_sigma_add_new_rule}
	\end{figure}
	Compared with the posterior sample distribution of $\tau_1$ in Fig. \ref{fig_v_bd9_4_up_tau}, the posterior sample distribution in Fig. \ref{fig_v_bd9_4_up_tau_add_new_rule} is more conducive to the identification of the change point.
	Although there are still some sampling points around 1200 seconds, most of the sample number is below 1000, which has little effect.
	The posterior distribution of $\tau_2$ has slightly changed. 
	There are a few sampling points around 1750 s, which are not enough to affect the identification of change points.
	From the comparison between Fig. \ref{fig_v_bd9_4_up_mu} and Fig. \ref{fig_v_bd9_4_up_mu_add_new_rule}, it can be seen that the secondary peak of $\mu_1$ almost disappears.
	However, there are still some sample points \textcolor{r_s}{that} deviate from the main peak.
	To reduce the influence of these sampling points, the median value of the sample is used as the final estimation of \textbf{$\mu$}, and $\mu_0$, $\mu_1$ and $\mu_2$ are obtained as -1461.18 mm, -1482.37 mm and -1509.09 mm respectively.
	The two displacements obtained by these means are -21.19 mm and -26.72 mm, respectively, and the displacements measured in Table \ref{tab_measured_height_9_4} are -21.3 mm and -19.6 mm respectively.  
	The displacement difference between the two methods at the two change points is 0.11 mm and 7.12 mm, respectively. 
	The larger displacement error at $\tau_2$ is mainly due to the incompletely controllable experimental equipment. 
	\textcolor{r_s}{
		 The number of satellites, GDOP, SNR, and multipath are shown in Fig. \ref{fig_v_ndop_snrmp_9_4}. The number of satellites and GDOP changed at $\tau_2$, which may be caused by the shielding of the antenna during operation.}	
	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{ndop_snrmp_9_4}
		\caption{Number of satellites, GDOP, SNR, multipath of experiment 2.}
		\label{fig_v_ndop_snrmp_9_4}
	\end{figure} 
	But on the whole, using the proposed method, the displacement extraction accuracy in the experiment can reach less than 2 mm. However, as mentioned in the simulation experiment, the accuracy of displacement extraction in practical application also depends on the number of available samples near the change point.
	It can be seen from Fig. \ref{fig_v_bd9_4_up_sigma_add_new_rule} and Fig. \ref{fig_v_bd9_4_up_sigma} that the secondary peak of $\sigma$ posterior distribution has been significantly weakened.

>>>>

		\title{\textcolor{r_s}{Displacement Detection Based on Bayesian Inference from GNSS Kinematic Positioning for Deformation Monitoring}}

		%% use optional labels to link authors explicitly to addresses:
		%% \author[label1,label2]{}
		%% \address[label1]{}
		%% \address[label2]{}
		\author[a]{Nan Shen}
		\author[a]{Liang Chen\corref{mycorrespondingauthor}}
		\cortext[mycorrespondingauthor]{Corresponding author}
		\ead{l.chen@whu.edu.cn}
		\author[a]{Ruizhi Chen}
		\address[a]{State Key Laboratory of Information Engineering in Surveying, Mapping and Remote Sensing, Wuhan University, Wuhan 430000, PR China}
		\begin{abstract}
		Displacement is an important parameter in engineering analysis in structural mechanics and geomechanics.
		For decades, displacement detection based on the Global navigation satellite system (GNSS) has increasingly been important for a wide range of applications, from landslide monitoring, subsidence survey, to industrial measurement. 
%		Most of the GNSS-based displacement detection methods in these applications are based on GNSS long-term static positioning results.
%		With the development of the Internet of Things (IoT), high-precision GNSS positioning, and GNSS-related transmission protocol, kinematic positioning results can be transmitted to the cloud in real-time.
		However, due to the influence of measurement noise, it is still a challenge to identify and extract displacement from GNSS kinematic positioning results.
		To resolve this, we propose a novel displacement detection approach with the purpose of identifying and extracting displacement from GNSS kinematic positioning.
		Specifically, we use the Bayesian inference to obtain the displacement change time from the coordinate time series of GNSS kinematic positioning. 
		%The likelihood function of the observation and the prior distribution of the parameters to be estimated are provided.
		%Finally, Bayesian inference was implemented by Markov Chain Monte Carlo (MCMC) sampling.
		By investigating the posterior distribution of the designed change point parameter, we can identify the change points.
		Furthermore, we derive the mean value from the posterior distribution of the mean parameter, and further obtain the displacement.
		Results from simulation and field experiments have demonstrated the effectiveness and flexibility of the proposed method.
		For significant displacement, it can be clearly identified; for small displacement, it can be identified by adding an interval constraint prior. The accuracy of \textcolor{r_s}{vertical} displacement extraction from GNSS real-time kinematic positioning can reach within 2 mm in 15 minutes.		
		\end{abstract}

@@

	% 仿真实验中不同基于索引检测方法的指标值如图6所示。
	% 从中可以看出不同探测方法所采用的指标的数值范围不一致，但在所设计的突变处很明显。
	%  然而，想基于这些指标值自动将这些突变点识别出来，还需要额外的工作。
	%  另外，这些方法设计之初为了探测突变点，并未涉及位移提取。
	%  有学者，基于设计了基于这些指标的突变探测和位移提取方法，但实时过程复杂。
	%  相比而言，本文提出的方法是一种简单直接易于实现的一站式方法。
	\textcolor{r_s}{
		Detection values of different index-based detection methods in the simulation experiment are shown in Fig. \ref{fig_v_sim_idx}.
	}
	It can be seen that the numerical range of indicators used by different \textcolor{r_s}{index-based} detection methods is not consistent, but all are obvious at the designed abrupt point. \textcolor{r_s}{These detection values can be obtained in real-time from the GNSS kinematic positioning results.} However, to automatically identify these abrupt points based on these \textcolor{r_s}{detection} values, additional work is required, such as setting a certain threshold  \textcolor{r_s}{or detection window\cite{shen_shortterm2021}}. In addition, these methods were originally designed to detect abrupt points without involving displacement extraction. \textcolor{r_s}{
	Although there are improved methods of abrupt detection and displacement extraction based on these indicators, the implementation process is complex\cite{shen_shortterm2021}.
	} In contrast, the method proposed in this work is a simple, straightforward, and easy-to-implement one-stop method.
	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_sigma_sim_simple}
		\caption{Histogram of posterior sample of $\sigma$ in the simulation experiment.}
		\label{fig_v_sigma_sim_simple}
	\end{figure} 
	\begin{figure}[htbp]
	\centering
	\includegraphics[scale=0.45]{v_sim_idx}
	\caption{\textcolor{r_s}{Detection values of different index-based detection methods in the simulation experiment.}}
	\label{fig_v_sim_idx}
	\end{figure} 
	\subsection{Field Experiments}
	The experiments were carried out on the roof of a building on the campus of Wuhan University, and the equipment deployment is shown in Fig. \ref{fig_v_field_exp_config}. 
	A hard plank was pressed with large stones to ensure that the plank remains as fixed as possible during moving the object hanging on the plank. 
	One receiver antenna was fixed on the plank as a rover, and the other receiver antenna was installed on a tripod beside it as the base station. 
	Both antennas were connected to BD992 OEM boards on the table, and the OEM boards were connected to the laptops for data collection. 
	As shown in subgraphs (c) and (d), the height of the antenna was measured with a tape before and after each movement of the object hanging on the plank. 
	\textcolor{r_s}{
		The minimum scale of the tape is 1 mm, that is, the accuracy of the tape is 1 mm, and the estimated reading is 0.1 mm.
		Take five readings for each measurement to ensure the accuracy and reliability of the data.
	}
	Besides, markers are made on the ground and on the antenna respectively to ensure that the same position was referenced for each measurement. 
	The sampling frequency of the GNSS receiver is set to 1 Hz. 
	We did two experiments, each lasting nearly 45 minutes. 
	During the experiment, the object hanging on the board was manually moved several times.
	The displacement amplitude of the second experiment is smaller than that of the first experiment.
	The GNSS observation data collected above are processed by the open-source software RTKLIB\cite{takasu2011rtklib}. 
	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.5]{v_field_exp_config}
		\caption{Filed experiment configuration. (a) Overview; (b) Working platform; (c) Displacement control platform; (d) Displacement measurement by tape. }
		\label{fig_v_field_exp_config}
	\end{figure}

@@

	For such a short baseline, most of the errors can be eliminated by the double-difference observation. 
	As can be seen from Fig. \ref{fig_v_bd9_3_up_ts}, there are still some unmodeled errors, such as the multipath error that have not been eliminated. 
	\textcolor{r_s}{The RTK positioning results are served as the input of displacement detection}, and Bayesian inference is implemented by the MCMC sampling. 
	The histogram of the posterior sample of $\tau$ is shown in Fig. \ref{fig_v_bd9_3_up_tau}.
	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_bd9_3_up_tau}
		\caption{Posterior sample distribution of $\tau$ in field experiment 1.}
		\label{fig_v_bd9_3_up_tau}
	\end{figure} 
	From the posterior sample distribution of $\tau_2$ in Fig. \ref{fig_v_bd9_3_up_tau}, one of the change points can be identified as 1897 s. 
	According to the maximum value in the bar chart of the posterior sample of $\tau_1$, the change point is identified as 781 s.
	However, as can be seen from Fig. \ref{fig_v_bd9_3_up_tau}, there are two peaks in the posterior sample distribution of change point $\tau_1$.
	The main reason is that the displacement control device is not completely controllable, and the plank floats up and down when moving the object. 
	In addition, since the antenna is close to the ground, the antenna vibration caused by breeze or touch causes an increase in the multipath phase rate or fading frequency\cite{kelly2003characterization}. 
	The index values of different index-based detection methods in \textcolor{r_s}{the} field experiment 1 are shown in Fig. \ref{fig_v_exp1_idx}. At the abrupt point, each index value is no longer as clear as in the simulation experiment, which puts forward higher requirements for additional analysis of these indexes.
	The posterior sample histogram of the $\mu$ of each segment divided by the change point and the displacement measured by the tape are shown in Fig. \ref{fig_v_bd9_3_up_mu} and Table \ref{tab_measured_height_9_3}, respectively.
	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_exp1_idx}
		\caption{\textcolor{r_s}{Detection values of different index-based detection methods in field experiment 1.}}
		\label{fig_v_exp1_idx}
	\end{figure} 
	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_bd9_3_up_mu}
		\caption{Histogram of posterior sample of $\mu$ in field experiment 1.}
		\label{fig_v_bd9_3_up_mu}
	\end{figure} 
	\begin{table}[htbp]
		\centering
		%	\fontsize{6.5}{8}\selectfont
		\begin{threeparttable}
			\caption{Measured height before and after each movement of the object hanging on the plank in field experiment 1, unit (mm).}
			\label{tab_measured_height_9_3}
			\begin{tabular}{ccccccccc}
				\toprule
				&&&\textbf{1}&\textbf{2}&\textbf{3}&\textbf{4}&\textbf{5}&\textbf{mean}\cr
				\midrule
				\multirow{3}*{Step 1} 
				& & ${h_0}$    &371.0&370.9&370.9&371.1&370.9&370.96\\
				& & ${h_1}$    &341.0&341.1&341.5&341.9&341.0&341.30\\
				& & $\Delta h$ & -30.0& -29.8& -29.4& -29.2& -29.9&-29.66\\
				\hline
				\multirow{3}*{Step 2} 
				& & ${h_0}$    &340.5&340.1&340.0&340.0&340.1&340.14\\
				& & ${h_1}$    &313.0&312.9&312.9&313.0&313.0&312.96\\
				& & $\Delta h$ &-27.5& -27.2& -27.1& -27.0& -27.1& -27.18\\
				\bottomrule
			\end{tabular}
		\end{threeparttable}
	\end{table}

	The $\mu_0$, $\mu_1$, and $\mu_2$ obtained by the mean of the posterior samples are -1446.03 mm, -1474.11 mm, and -1489.83 mm, respectively, and the two displacements obtained by the difference of these mean values are -28.08 mm, -15.72 mm, respectively. The two displacements measured by tape are -29.66 mm and -27.18 mm respectively. 
	To our surprise, the displacement difference between the two methods at the two change points is 1.58 mm and 11.46 mm, respectively. 
	The main reason is that the displacement control device is not fully controllable.
\textcolor{r_s}{
	As can be seen from Fig. \ref{fig_v_bd9_3_up_ts}, the time series fluctuates obviously near the abrupt displacement. To explore the possible causes, the number of satellites, geometric dilution of precision (GDOP), signal-to-noise ratio (SNR), and multipath are shown in Fig. \ref{fig_v_ndop_snrmp_9_3}. When the displacement occurs, the number of satellites and GDOP change, especially at $\tau_2$, which may be the reason for the inconsistency between the reference displacement and the estimated displacement.
	The SNR and multipath have also changed when the displacement takes place, possibly due to antenna vibration caused by touch or wind.}

	As shown in Fig. \ref{fig_v_bd9_3_up_sigma}, the estimated value of $\sigma$ is 12.58 mm through the posterior sample mean of $\sigma$.
	%我们发现此处变点后验样本中的两个峰值对于均值和标准差中没有出现。
	%主要原因是变点的峰值距离很近，对于划分的段没有很明显的影响，因此对后验均值和标准差的浮动没有很大影响。
	%而在现实中，这种情况是会发生的，例如滑坡或者沉降，整个位移变化过程需要一定的时间，存在多个变化点。
	%然而，我们可能更加关注主要变化点，后面通过加入额外先验来提升主要变化点的识别，弱化次要变化点。
	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{ndop_snrmp_9_3}
		\caption{\textcolor{r_s}{Number of satellites, GDOP, SNR, multipath of experiment 1.}}
		\label{fig_v_ndop_snrmp_9_3}
	\end{figure} 
	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_bd9_3_up_sigma}
		\caption{Histogram of posterior \textcolor{r_s}{samples} of $\sigma$ in field experiment 1.}
		\label{fig_v_bd9_3_up_sigma}
	\end{figure} 
	Different from the posterior sample distribution of $\tau$, there is only one peak value in the posterior sample distribution of $\mu$ and $\sigma$.
	The main reason is that the interval of the two peaks is very close, which has little influence on the posterior mean and standard deviation.
	In reality, multiple change points exist, such as multiple displacements in a short period in the process of landslide or settlement.
	However, more attention is paid to the primary change points.
	By adding a prior to the model to improve the identification of the primary change points, and weaken the influence of secondary change points will be discussed later.
	\subsubsection{Field Experiment 2}%rover_bd9_4 part(650)
	This experiment is similar to the previous one except that the displacement amplitude is smaller. 
	The coordinate time series is obtained by RTKLIB with the same processing strategy as the previous experiment, and the up component of the time series is shown in Fig. \ref{fig_v_bd9_4_up_ts}. 
	In this experiment, the displacement measured by tape is shown in Table \ref{tab_measured_height_9_4}.

@@

	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_bd9_4_up_tau_add_new_rule}
		\caption{Posterior sample distribution of $\tau$ in field experiment 2 with an interval constraint prior.}
		\label{fig_v_bd9_4_up_tau_add_new_rule}
	\end{figure} 
	\begin{figure}[htbp]
	\centering
	\includegraphics[scale=0.45]{v_exp2_idx}
	\caption{\textcolor{r_s}{Detection values of different index-based detection methods in field experiment 2.}}
	\label{fig_v_exp2_idx}
	\end{figure} 
	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_bd9_4_up_mu_add_new_rule}
		\caption{Histogram of posterior sample of $\mu$ in field experiment 2 with an interval constraint prior.}
		\label{fig_v_bd9_4_up_mu_add_new_rule}
	\end{figure} 
	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_bd9_4_up_sigma_add_new_rule}
		\caption{Histogram of posterior \textcolor{r_s}{samples} of $\sigma$ in field experiment 2 with an interval constraint prior.}
		\label{fig_v_bd9_4_up_sigma_add_new_rule}
	\end{figure}
	Compared with the posterior sample distribution of $\tau_1$ in Fig. \ref{fig_v_bd9_4_up_tau}, the posterior sample distribution in Fig. \ref{fig_v_bd9_4_up_tau_add_new_rule} is more conducive to the identification of the change point.
	Although there are still some sampling points around 1200 seconds, most of the sample number is below 1000, which has little effect.
	The posterior distribution of $\tau_2$ has slightly changed. 
	There are a few sampling points around 1750 s, which are not enough to affect the identification of change points.
	From the comparison between Fig. \ref{fig_v_bd9_4_up_mu} and Fig. \ref{fig_v_bd9_4_up_mu_add_new_rule}, it can be seen that the secondary peak of $\mu_1$ almost disappears.
	However, there are still some sample points \textcolor{r_s}{that} deviate from the main peak.
	To reduce the influence of these sampling points, the median value of the sample is used as the final estimation of \textbf{$\mu$}, and $\mu_0$, $\mu_1$ and $\mu_2$ are obtained as -1461.18 mm, -1482.37 mm and -1509.09 mm respectively.
	The two displacements obtained by these means are -21.19 mm and -26.72 mm, respectively, and the displacements measured in Table \ref{tab_measured_height_9_4} are -21.3 mm and -19.6 mm respectively.  
	The displacement difference between the two methods at the two change points is 0.11 mm and 7.12 mm, respectively. 
	The larger displacement error at $\tau_2$ is mainly due to the incompletely controllable experimental equipment. 
	\textcolor{r_s}{
		 The number of satellites, GDOP, SNR, and multipath are shown in Fig. \ref{fig_v_ndop_snrmp_9_4}. 
		 From the SNR and multipath, it can be seen that the quality of the observation data on the right side of $\tau_2$ is better than that on the left side.}
	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{ndop_snrmp_9_4}
		\caption{\textcolor{r_s}{Number of satellites, GDOP, SNR, multipath of experiment 2.}}
		\label{fig_v_ndop_snrmp_9_4}
	\end{figure} 
	But on the whole, using the proposed method, the displacement extraction accuracy in the experiment can reach less than 2 mm. However, as mentioned in the simulation experiment, the accuracy of displacement extraction in practical application also depends on the number of available samples near the change point.
	It can be seen from Fig. \ref{fig_v_bd9_4_up_sigma_add_new_rule} and Fig. \ref{fig_v_bd9_4_up_sigma} that the secondary peak of $\sigma$ posterior distribution has been significantly weakened.
